We will use this section to discuss another implementation possibility as well as how we could improve our solution.

\paragraph{}
One of the things we were told is that we could have transpiled tool to javascript, generated a source map file and then used a native debugger such as the Chrome developper tools. While this approach may seem beneficial at first (we use a robust and full featured piece of GUI), it is limited and actually not suitable for our purpose. A source map is only a way to debug something that is meant to be run in a javascript environment. It depends on javascript's underlying types and does not allow a great deal of language-specific customization. \\On the other hand, we want the tool program to behave identically as in the JVM or anywhere else --- and this even when types are pushed to their limits. Also, our approach allows to integrate the compiler and the debugger in a coherent environment which is much more comfortable to use.

\paragraph{}
We are quite satisfied with the solution we came up with. We believe that with this tool (no pun intended), we would have gained massive time when writing test programs. The feedback loop of writing code, finding bugs, killing them and writing code again would have been much tighter with everything contained in one single interface. We acknowledge that it is far from being perfect and we have a few ideas of things that could have been further improved.

\begin{itemize}
\item The VM should run in a separate thread than the UI. This allows the interface to stay responsive even when the program is stucked. Currently, if a program loops indefinitely, the web page has to be closed. It is not a trivial modification and involves some work with HTML5 web workers and messaging --- we believe this was a little out of the scope of this extension.
\item Although the core software involved here works well, the UI is still pretty rough and could have been improved a bit. For instance, we could make the variables tree not to collapse each time we step over an instruction.
\item Some debugging related features could be added: watch the value of expressions, change the value of variables from the interface, set conditional breakpoints...
\end{itemize}